Replicator-mutator and noise-perturbed replicator dynamics

### 2015-08-11 snippets/data_exploration/data_exploration_tmp.Rmd
started on version 4

data$converged = data$Iterations < 201
data$convex = data$Speaker.Convex.Cat

ds = data[,c("Number.of.states", "Impairment", "Tolerance", 
             "Speaker.entropy", "Hearer.entropy",
             "Speaker.Voronoiness", "Hearer.Voronoiness",
             "Expected.utility",
             "convex", "converged"
             )]

dms = summarySE(dm, groupvars = c("Number.of.states", "Impairment", "Tolerance", "variable"), measurevar="value")
dsub = dms
dsub$Number.of.states = factor(dsub$Number.of.states)

myLabeller <- function(var, value){
    value <- as.character(value)
    if (var=="variable") { 
        value[value=="Speaker.entropy"] <- "entropy sen"
        value[value=="Hearer.entropy"] <- "entropy rec"
        value[value=="Speaker.Voronoiness"] <- "Voronoiness sen"
        value[value=="Hearer.Voronoiness"] <- "Voronoiness rec"
        value[value=="Expected.utility"] <- "expected utility"
    }
    return(value)
}

pd <- position_dodge(.01)
mysize = 1.65
sp = ggplot(dsub, aes(x=Impairment, y=value, color = Number.of.states, shape=Number.of.states, linetype=Number.of.states)) + 
    geom_line(color="gray", position = pd) + xlab("imprecision") +
     geom_point(position = pd, size = mysize) +
     geom_errorbar(aes(ymin=value-ci, ymax=value+ci), width=0, position=pd) +
    scale_shape_discrete(name = "# states", guide = guide_legend()) +
    scale_linetype_discrete(name = "# states", guide = guide_legend()) +
    scale_color_discrete(name = "# states", guide = guide_legend()) +
    theme(legend.position="top")

sp = sp + facet_grid(variable ~ Tolerance, scales="free", labeller=myLabeller)

sp + facet_grid(. ~ sex, labeller=mf_labeller)
show(sp)

ggsave(sp, file = "paper/plots/MeanMetrics2.pdf", width=8, height = 10)

@@

ggsave(sp, file = "paper/version_02/plots/MeanMetrics3.pdf", width=5, height = 5.5)

@@

pd <- position_dodge(.05)
sp = ggplot(dms, aes(x=factor(Impairment), y = value, group = variable, shape = variable, linetype = variable)) 
sp = sp + geom_line(position = pd, color = "grey") + geom_point(position = pd)
sp = sp + facet_grid(Number.of.states ~ Tolerance, scales="free") + ylab("proportion") + xlab("imprecision") +
  scale_shape_discrete(name = "property") +
  scale_linetype_discrete(name = "property")
show(sp)
ggsave(sp, file = "paper/plots/CategoricalMeasures.pdf", width=8, height = 5)

>>>>

# ```{r message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
# 
# data$converged = data$Iterations < 201
# data$convex = data$Speaker.Convex.Cat
# 
# ds = data[,c("Number.of.states", "Impairment", "Tolerance", 
#              "Speaker.entropy", "Hearer.entropy",
#              "Speaker.Voronoiness", "Hearer.Voronoiness",
#              "Expected.utility",
#              "convex", "converged"
#              )]
# 
# dm = melt(ds, id.vars = c("Number.of.states", "Impairment", "Tolerance"))
# 
# dms = summarySE(dm, groupvars = c("Number.of.states", "Impairment", "Tolerance", "variable"), measurevar="value")
# dsub = dms
# dsub$Number.of.states = factor(dsub$Number.of.states)
# 
# myLabeller <- function(var, value){
#     value <- as.character(value)
#     if (var=="variable") { 
#         value[value=="Speaker.entropy"] <- "entropy sen"
#         value[value=="Hearer.entropy"] <- "entropy rec"
#         value[value=="Speaker.Voronoiness"] <- "Voronoiness sen"
#         value[value=="Hearer.Voronoiness"] <- "Voronoiness rec"
#         value[value=="Expected.utility"] <- "expected utility"
#     }
#     return(value)
# }
# 
# 
# pd <- position_dodge(.01)
# mysize = 1.65
# sp = ggplot(dsub, aes(x=Impairment, y=value, color = Number.of.states, shape=Number.of.states, linetype=Number.of.states)) + 
#     geom_line(color="gray", position = pd) + xlab("imprecision") +
#      geom_point(position = pd, size = mysize) +
#      geom_errorbar(aes(ymin=value-ci, ymax=value+ci), width=0, position=pd) +
#     scale_shape_discrete(name = "# states", guide = guide_legend()) +
#     scale_linetype_discrete(name = "# states", guide = guide_legend()) +
#     scale_color_discrete(name = "# states", guide = guide_legend()) +
#     theme(legend.position="top")
# 
# sp = sp + facet_grid(variable ~ Tolerance, scales="free", labeller=myLabeller)
# 
# sp + facet_grid(. ~ sex, labeller=mf_labeller)
# show(sp)
# 
# ggsave(sp, file = "paper/version_04/plots/MeanMetrics2.pdf", width=8, height = 10)
# 
# ```

@@

ggsave(sp, file = "paper/version_04/plots/MeanMetrics3.pdf", width=5, height = 5.5)

@@

pd <- position_dodge(.05)
sp = ggplot(dms, aes(x=factor(Impairment), y = value, group = variable, shape = variable, linetype = variable)) 
sp = sp + geom_line(position = pd, color = "grey") + geom_point(position = pd)
sp = sp + facet_grid(Number.of.states ~ Tolerance, scales="free") + ylab("proportion") + xlab("imprecision") +
  scale_shape_discrete(name = "property") +
  scale_linetype_discrete(name = "property")
show(sp)
ggsave(sp, file = "paper/version_04/plots/CategoricalMeasures.pdf", width=8, height = 5)
